Forcing for Isabelle

### 2018-12-18 LICS/forcing.tex
un poco de fabstracts

\fbox{poner acá lo de formal abstracts y el locale \texttt{forcing\_thms}}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Separation_In_MG"
%%% ispell-local-dictionary: "american"
%%% End:

>>>>

The presentation of the Fundamental Theorems of Forcing in a locale
can be regarded as a \emph{formal abstract} as in the project
envisioned by Hales \cite{fabstracts}, where  statements of
mathematical theorems proven in the literature are posed in a language
that is both human- and computer-readable. The point is to take
particular care so that, v.g., there are no missing hypothesis, so it
is possible to take this statement as firm ground on which start a
formalization of a proof.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Separation_In_MG"
%%% ispell-local-dictionary: "american"
%%% End:
